Draft

### 2024-07-02 Bootstrap.Rmd
Before leaving ENSAI

@@

```{r}
# Function to produce a local variable
source("~/work/Sim_article2024/Useful_functions/Circle.R")
```

```{r}
rho_boot <- tibble(.rows = n)
for (c in 1:B) {
  # assign(ech_, df_boot[c])
  a <- c()
  for (i in 1:n) {
    a <- append(a, circle_nb(df_boot[i, (2*c)-1], df_boot[i, 2*c], R))
  }
  rho_boot <- rho_boot %>% add_column(new_col = a)
  colnames(rho_boot)[c] <- paste("est", c, sep = "")
}

# List of estimated totals thus obtained from each sample
est_boot <- c()
for (c in 1:B) {
  est_boot <- append(est_boot, sum((rho_boot[c])/p))
}

est_boot <- sort(est_boot)
```

```{r}
rm(a, c, i, col_names, col_)
```

@@

```{r}
rho_init <- tibble(.rows = n)
# col_names <- c()
# for (c in 1:B) {
#   col_ <- paste("est", c, sep = "")
  # ech_ <- paste("ech", c, sep = "")
  # assign(ech_, df_boot[c])
  a <- c()
  for (i in 1:n) {
    # loc_var <- 
    a <- append(a, circle_nb(random_points[i, 1], random_points[i, 2], R))
    }
  # a <- circle(df_boot[(2*c)-1], df_boot[2*c], R)
  # print(col_)
  rho_init <- rho_init %>% add_column("ech_init" = a) # 
  # col_names <- append(col_names, col_)
  # colnames(rho_boot) <- col_names
# }

# colnames(rho_boot) <- "ech_init"

# 3rd step: List of estimated totals thus obtained from each sample
est_init <- c()

est_tot <- sum((rho_init[1])/p)
est_init <- append(est_init, est_tot)

est_init <- sort(est_init)
```

@@

>>>>

```{r}
# Functions to produce a local variable
source("~/work/Sim_article2024/Useful_functions/Circle.R")
```

@@

# Estimations and confidence intervals based on the bootstrap samples

## With one single circle

```{r}
# Estimation of the total number of trees for each bootstrap sample
est_boot <- c()
for (c in 1:B) {
  a <- c()
  for (i in 1:n) {
    a <- append(a, circle_nb(df_boot[i, (2*c)-1], df_boot[i, 2*c], R))
  }
  est_boot <- append(est_boot, sum(a/p))
}
est_boot <- sort(est_boot)
```

```{r}
rm(a, c, i)
```

@@

```{r}
a <- c()
for (i in 1:n) {
  a <- append(a, circle_nb(random_points[i, 1], random_points[i, 2], R))
}

# Estimated total thus obtained from the initial sample
est_init <- sum(a/p)

@@

## With three circles

```{r}
### With 3 circles as described in Trinh et alii (2024), page 8

est_boot_3 <- c()
for (c in 1:B) {
  a <- c()
  for (i in 1:n) {
    a <- append(a, circle3_nb(df_boot[i, (2*c)-1], df_boot[i, 2*c], 15, 9, 6))
  }
  est_boot_3 <- append(est_boot_3, sum(a/p))
}

est_boot_3 <- sort(est_boot_3)

```{r}
# Confidence Interval based on the percentile approach
lim_inf <- est_boot_3[floor(B*2.5/100)]
lim_sup <- est_boot_3[B - floor(B*2.5/100)]
cat("Un intervalle de confiance à 95% par la méthode des percentiles est : [", lim_inf, ";", lim_sup, "]" )
```

```{r}
a <- c()
for (i in 1:n) {
  a <- append(a, circle3_nb(random_points[i, 1], random_points[i, 2], 15, 9, 6))
}

# Estimated total thus obtained from the initial sample
est_init_3 <- sum(a/p)

```{r}
# Confidence Interval based on the reverse percentile approach
cat("Un intervalle de confiance à 95% par la méthode des reverse percentiles est : [", est_init_3*2 - lim_sup, ";", est_init_3*2 - lim_inf, "]" )
```

```{r}
est_boot3 <- c()
for (c in 1:B) {
  a <- c()
  for (i in 1:n) {
    a <- append(a, circle_nb(df_boot[i, (2*c)-1], df_boot[i, 2*c], 15))
  }
  est_boot3 <- append(est_boot3, sum(a/p))
}

est_boot3 <- sort(est_boot3)

### 2024-07-02 Draft.Rmd
Before leaving ENSAI

>>>>

```{r}
# To evaluate complexity
install.packages("cyclocomp")
```

```{r}
library(cyclocomp)
```

```{r}
cyclocomp(circle_nb) # 1
```

```{r}
# Probably less efficient than the version actually used in Bootstrap.Rmd
start.time <- Sys.time()

rho_boot <- tibble(.rows = n)
for (c in 1:B) {
  # assign(ech_, df_boot[c])
  a <- c()
  for (i in 1:n) {
    a <- append(a, circle_nb(df_boot[i, (2*c)-1], df_boot[i, 2*c], R))
  }
  rho_boot <- rho_boot %>% add_column(new_col = a)
  colnames(rho_boot)[c] <- paste("est", c, sep = "")
}

# List of estimated totals thus obtained from each sample
est_boot <- c()
for (c in 1:B) {
  est_boot <- append(est_boot, sum((rho_boot[c])/p))
}

est_boot <- sort(est_boot)

end.time <- Sys.time()
time.taken1 <- end.time - start.time

time.taken1

# Time difference of 52.57304 secs
# Time difference of 52.57391 secs
# Time difference of 54.01066 secs
```

```{r}
### More efficient??? Slower than the above version

start.time <- Sys.time()

rho_boot <- tibble(.rows = n)
for (c in 1:B) {
  # assign(ech_, df_boot[c])
  a <- c()
  for (i in 1:n) {
    if(circle_nb(df_boot[i, (2*c)-1], df_boot[i, 2*c], R) != 0){
    a <- append(a, circle_nb(df_boot[i, (2*c)-1], df_boot[i, 2*c], R))
    }
  }
  a2 <- append(a, rep(0, n-length(a)))
  rho_boot <- rho_boot %>% add_column(new_col = a2)
  colnames(rho_boot)[c] <- paste("est", c, sep = "")
}

# List of estimated totals thus obtained from each sample
est_boot2 <- c()
for (c in 1:B) {
  est_boot2 <- append(est_boot2, sum((rho_boot[c])/p))
}

est_boot2 <- sort(est_boot2)

end.time <- Sys.time()
time.taken2 <- end.time - start.time

time.taken2

# Idea: "a" is sparse: let's simplify by shortening it
# Time difference of 1.526216 mins :(
# Modif: still not good
# Time difference of 1.45528 mins

# That one works (and still too long)
# Time difference of 1.126081 mins
# Time difference of 1.094733 mins
```

```{r}
# For the version actually used in Bootstrap.Rmd
start.time <- Sys.time()

end.time <- Sys.time()
time.taken3 <- end.time - start.time

time.taken3

# Time difference of 54.02127 secs
# Time difference of 50.4839 secs
# Time difference of 53.94593 secs
```
